lasso

### 2023-04-24 code/analysis_code/stats/5_multi_variate_models/random_forest_models.qmd
addressing Raqi's comments

```{r}
rf_pred_plot <- ggplot(rf_residuals, 
                          aes(x = copies_mL, 
                              y = .pred)) + 
  geom_point() + 
  labs(title = "Predictions vs Actual: Random Forest", 
       x = "Copies/mL Actual", 
       y = "Copies/mL Prediction")
rf_pred_plot

@@

```{r}
rf_pred_plot <- ggplot(rf_residuals, 
                          aes(x = copies_mL, 
                              y = .pred)) + 
  geom_point() + 
  labs(title = "Predictions vs Actual: Random Forest", 
       x = "Copies/mL Actual", 
       y = "Copies/mL Prediction")
rf_pred_plot

@@

```{r}
rf_pred_plot <- ggplot(rf_residuals, 
                          aes(x = copies_mL, 
                              y = .pred)) + 
  geom_point() + 
  labs(title = "Predictions vs Actual: Random Forest", 
       x = "Copies/mL Actual", 
       y = "Copies/mL Prediction")
rf_pred_plot

>>>>

```{r}
rf_pred_plot <- ggplot(rf_residuals, 
                          aes(x = copies_mL, 
                              y = .pred)) + 
  geom_point() + 
  labs(title = "Blind Oso: Predictions vs Actual: Random Forest", 
       x = "Copies/mL Actual", 
       y = "Copies/mL Prediction") +
  theme_bw()
rf_pred_plot

rf_residual_plot <- ggplot(rf_residuals, 
                              aes(y = .resid, 
                                  x = .pred)) + 
  geom_point() + 
  labs(title = "Blind Oso: Predictions vs Residuals: Random Forest", 
       x = "Copies/mL Prediction", 
       y = "Residuals")
plot(rf_residual_plot) + #view plot
  theme_bw()
```

@@

```{r}
rf_pred_plot <- ggplot(rf_residuals, 
                          aes(x = copies_mL, 
                              y = .pred)) + 
  geom_point() + 
  labs(title = "Canals: Predictions vs Actual: Random Forest", 
       x = "Copies/mL Actual", 
       y = "Copies/mL Prediction") +
  theme_bw()
rf_pred_plot

@@

```{r}
rf_pred_plot <- ggplot(rf_residuals, 
                          aes(x = copies_mL, 
                              y = .pred)) + 
  geom_point() + 
  labs(title = "Gulf: Predictions vs Actual: Random Forest", 
       x = "Copies/mL Actual", 
       y = "Copies/mL Prediction") + 
  theme_bw()
rf_pred_plot
